---
title: "Write R programs for simulations from probability models and randomization-based experiments."
description: |
author:
  - name: Courtney Rose
preview: experiments.png
output:
  distill::distill_article:
    self_contained: false
---

```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(broom)
library(infer)
library(lmboot)
library(MASS)
midwest
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### 1. I can write a function that accomplishes a common analysis task.

```{r calc_range, echo=TRUE}
calculate_range <- function(x){
  range_results <- range(x)
  range <- range_results[2] - range_results[1]
  return(range)
}
```

Calculating range is a common analysis task that I learned how to create a function for this semester.  

### 2. I can apply a function to groupings within a data source.
```{r apply_function, echo=TRUE, include=TRUE}
calculate_range(midwest$poptotal)
```
```{r apply_function2, echo=TRUE, include=TRUE}
calculate_range(1:10)
```

### 3. I can implement resampling methods to make conclusions about data.

For this objective, I am going to bring in a new data set to show that I have accomplished this objective throughout the course. I plan to use bootstrapping, or sampling without replacement, to do a one-way ANOVA to understand if there is a difference between the midwest state's population of people living in poverty.

```{r bootstrap, echo=TRUE}
set.seed(19990502)
ANOVA <- ANOVA.boot(poppovertyknown~
                      as.factor(state),
                    data=midwest, 
                    B = 10000)
ANOVA$`p-values`
```
For this example, I did a one-way ANOVA to decide if there was a difference in means between the states of the amount of people that are living in poverty. I set it up to resample 10000 times, got an insignificant p-value, meaning that there is no evidence to suggest that there is a significant difference between each state's amount of people living in poverty.


### 4. I can use common probability distributions to simulate data and explore statistical ideas.

I learned from this [video](https://www.youtube.com/watch?v=tzz4flrajr0) that was attached to Chapter 20 of the [R Programming for Data Science](https://bookdown.org/rdpeng/rprogdatascience/simulation.html) by Roger Peng. 

Random Number Generation:

```{r normal, echo=TRUE}
set.seed(34)
x <- rnorm(15)
x
```

Generating a random number from a normal distribution, 
with a mean of 30 and standard deviation of 4:

```{r random, echo=TRUE}
set.seed(34)
x <- rnorm(15, mean=30, sd=4)
summary(x)
```



I learned the next step from [this video](https://www.youtube.com/watch?v=p7kSSSsv4ms) for random numbers from a linear model.

Generate random number from a normal linear model, where intercept = 1 and the coefficient for X1 = 2.

```{r linearmod, echo=TRUE}
set.seed(34)
x <- rnorm(100)
e <- rnorm(100, 0, 2)
y <- 1 + 2*x + e
summary(y)
plot(x, y)
```

This proves that I can explore statistical ideas through these probaility distributions. I definitely still need to look this up for help on how to do it, but I believe that I know how to play around with it enough to cover this subobjective. 

### 5. I can fit a regression model for descriptive analysis.

I did a multiple regression model to predict the poverty population, which I hope will demonstrate this subobjective. I used backwards selection to get a final model that only included predictors that were significantly contributing to the model. I believe that this is sufficient evidence for this subobjective, because I completed a multiple regression model for descriptive analysis.

```{r mult_reg, echo=TRUE}
mod_midwest <- lm(poppovertyknown ~ 
                    poptotal + 
                    popdensity + 
                    popwhite + 
                    popblack + 
                    popamerindian + 
                    popasian, 
                  data = midwest)
reduced_mod_midwest <- 
  stepAIC(mod_midwest, 
          direction = "backward")
summary(reduced_mod_midwest)
```



