---
title: "Create graphical displays  and numerical summaries of data for exploratory analysis and presentations."
description: |
author:
  - name: Courtney Rose
preview: graphs.png
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, echo=TRUE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(reshape2)
library(MASS)
data("midwest")
```

For this set of objectives, I am going to be using the midwest data set that is imported from the ggplot2 package. 

### 1. I can create tables  graph of numerical summaries that draw attention to important comparisons.

I am going to try to summarize some important facts by each midwest state. 

```{r num_sum, echo=TRUE}
midwest_sum <- midwest %>%
  group_by(state) %>%
  summarise(
    total_population = sum(poptotal),
    total_population_density = sum(poptotal) / sum(area),
    avg_white = sum(popwhite) / sum(poptotal),
    avg_black = sum(popblack) / sum(poptotal),
    avg_asian = sum(popasian) / sum(poptotal),
    avg_amerindian = sum(popamerindian) / sum(poptotal),
    avg_other = sum(popother) / sum(poptotal),
    avg_poverty = sum(poppovertyknown) / sum(poptotal)) %>%
  arrange(desc(total_population))

as_tibble(midwest_sum)
```


### 2. I can create graphical displays of data that highlight key features.

```{r graphs, echo= TRUE}
ggplot(data = midwest) +
  geom_boxplot(mapping = 
                 aes(x = state, 
                     y = poppovertyknown, 
                     color = state)) +
  coord_flip() + 
  scale_y_continuous(lim=c(0,300000), name = "Population living in Poverty") +
  labs(title = "Povery Population by State")
```
```{r graph2, echo=TRUE}
ggplot(data=midwest_sum, 
       aes(x=state, y=total_population_density, fill=state)) +
      geom_bar(stat="identity") + 
  scale_y_continuous(breaks=seq(0,5000000, by = 500000),
                     name = "Total Population Density") +
  scale_x_discrete(name = "Midwest State") +
  labs(title = "Population Density by State")
```

### 3. I can combine multiple graphical displays or numerical summaries into an effective data product.

```{r combine, echo=TRUE}
midwest$county <- reorder(midwest$inmetro, midwest$popdensity)
midwest$state <- reorder(midwest$state, -midwest$popdensity)
ggplot(midwest, aes(popdensity, inmetro)) + 
  geom_point() + 
  facet_grid(state ~ ., scales = "fixed") +
  scale_y_discrete(breaks=seq(0,1,by=1))
```



